Draft

### 2017-03-06 Draft/sections/misc-math.tex
[minor] Notes of a "centered coordinate" which takes 2 variables into 1.

But there is one pitfall that confuses me for a long time. Because:
\begin{align*}
    \int\dd{x}g(x)x\delta'(x) = -\int\dd{x}(g(x)+xg'(x))\delta(x)
    = -\int\dd{x}g(x)\delta(x)
\end{align*}
This lures me into believing
\begin{equation}
    x\delta'(x) = -\delta(x)
    \label{eq:xdp--d}
\end{equation}
Hence
\begin{equation}
    \delta'(x) = -\frac{\delta(x)}{x}
    \label{eq:dp--dx}
\end{equation}
While \ref{eq:xdp--d} is correct, \ref{eq:dp--dx} is of course wrong.
\subsection{A beautiful product for sine function}

@@

\subsection{Common Pitfalls}
\label{sec:Common Pitfalls}
    \subsubsection{Tensors}
    \label{sec:Tensors}

>>>>

But there is one pitfall that confuses me for a long time. Because:
\begin{align*}
    \int\dd{x}g(x)x\delta'(x) = -\int\dd{x}(g(x)+xg'(x))\delta(x)
    = -\int\dd{x}g(x)\delta(x)
\end{align*}
This lures me into believing
\begin{equation}
    x\delta'(x) = -\delta(x)
    \label{eq:xdp--d}
\end{equation}
Hence
\begin{equation}
    \delta'(x) = -\frac{\delta(x)}{x}
    \label{eq:dp--dx}
\end{equation}
While \ref{eq:xdp--d} is correct, \ref{eq:dp--dx} is of course wrong.

\textbf{Note}: This, in my opinion, is an argument against completely treating
$\delta(x)$ as a function.
\subsection{A beautiful product for sine function}

@@

\subsection{A centered coordinate making two variables into one}

This technique is found in p.126 of \cite{Altland2010}. It should be helpful in
a much broader context.

The original equation is:
\begin{equation}
    \partial^2 \phi = \partial_\phi V(\phi)
\end{equation}
with $\partial^2 = \partial^2_\tau + \partial^2_x$. We propose a change of
coordinate $r\equiv \sqrt{x^2+\tau^2}$. Then after careful calculation, one
finds:
\begin{align*}
    \partial_x &= \pm\frac{\sqrt{r^2-\tau^2}}{r}\partial_r \\
    \partial^2_x &= 
        \frac{1}{r^2}\left(\frac{\tau^2}{r}\partial_r +
        (r^2-\tau^2)\partial^2_r\right) 
\end{align*}
and similarly for $\partial_\tau$. They combine into:
\begin{equation}
    \partial^2 = 
        \frac{1}{r^2}\left(\frac{x^2+\tau^2}{r}\partial_r +
        (r^2-\tau^2+r^2-x^2)\partial^2_r\right)
    = \frac{1}{r}\partial_r + \partial^2_r
\end{equation}
Therefore, we have a new equation:
\begin{equation}
    \partial^2_r \phi = - \frac{1}{r}\partial_r\phi + \partial_\phi V(\phi)
\end{equation}
with a "friction force" of the form $-\frac{1}{r}\partial_r\phi$.
\subsection{Common Pitfalls}
\label{sec:Common Pitfalls}
    \subsubsection{Tensors}
    \label{sec:Tensors}
